---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bills

<!-- badges: start -->
<!-- badges: end -->

The goal of bills is to easily calculate the additional costs of taxes and tips when shopping or eating in British Columbia, Canada. The function PriceBC, within this package, allows to rapidly predict the final bill at restaurants or shops after accounting for the appropriate taxes and user-selected tips. 

## Installation

bills is not yet on CRAN, but it can be downloaded from this repository by running the following R command:

``` r
# install.packages("devtools")
devtools::install_github("hans-ghezzi/bills")
```
## Usage

This is a basic example which shows how to use the `PriceBC()` function:

```{r example}
library(bills)
PriceBC("Sale", PriceTag = 50)
```

This package allows users to specify the service offered, between Restaurants and Sale, which involve different tax brackets. Choosing the service "Restaurants" also includes the notorious "Tips", which are culturally expected in North America.


```{r}
PriceBC(type = "Restaurant", MealBill = 25, Tip = 10, AlcoholBill = 10)
```
